### 2015-07-08 narrative/qos.tex
editing....

\subsubsection{Resource Management}
\paragraph{Background:} There is an important connection between finding the resources
that can fulfill a particular request and the performance predictability of that request, and this demands
careful resource management strategies that can deal with placing and retrieving a large number of data 
chunks spread across the entire storage hierarchy. 
%This connection is particularly important for data retrieval 
%- in large scale storage systems, finding a resource to read can be a significant, if not dominant, 
%component of overall read latency. 
Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because they require a single entity that tracks updates in the system. 
Traditional file systems are good examples for this - most updates to files require updates 
to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, search for 
resources at request time. Pile systems allow very efficient writes because clients can write wherever
there is free space and there is very low bookkeeping overhead. However, unbounded search in pile systems
is possible, e.g., when it is unclear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
partitioning of the search space and a method to limit the search to a small number of partitions.

@@

More specifically, the coarseness of a search space partitioning limits the search time within 
a partition, i.e. finely partitioned search spaces require little or no search within a partition 
but offer little placement flexibility. Partitioning can also be fine in one dimension and coarse 
in another to allow flexibility where it is most needed while still ensuring fast finding. For 
example, a hash function can finely partition a low storage tier but each partition can extend 
across multiple tiers so that a search still has to occur in order to find a resource on a particular 
tier.  Specifically, we will address the following research questions:
\begin{itemize}
  \item Can we make any guarantees in a scalable decentralized system?; 
 \item  What quality of service metrics can be make guarantees on in a scalable
    way?;
  \item What kind of error rates will we have in our estimation and what error
    rates are acceptable?;
  \item How much will the qos scheduler, admission control, manager cost in
    terms of resources and time?;
  \item  How do we make the scheduler scalable with the size of the system?
\end{itemize}

@@

\begin{itemize}

@@

\end{itemize}

>>>>

\subsubsection{Resource Management}
\paragraph{Background:} There is an important connection between finding the resources
that can fulfill a particular request and the performance predictability of that request. As such, this demands
careful resource management strategies that can deal with placement and retrieval of 
a large number of data chunks spread across the entire storage hierarchy. 
%This connection is particularly important for data retrieval 
%- in large scale storage systems, finding a resource to read can be a significant, if not dominant, 
%component of overall read latency. 
Locating resources is a typical distributed systems problem. Centralized solutions are limited in their
scalability, because they require a single entity that tracks updates in the system. 
Traditional file systems are good examples for this - most updates to files require updates 
to their centrally maintained block allocation tables. 
The opposite of file systems are ``pile'' systems, which, instead of keeping track of updates, search for 
resources at request time. Pile systems allow very efficient writes because clients can write wherever
there is free space and there is very low bookkeeping overhead. However, unbounded search in pile systems
is possible, e.g., when it is unclear whether the resource actually exists. 
Methods to make searches more efficient without reverting to centralized bookkeeping usually involves 
partitioning of the search space and a method to limit the search to a small number of partitions.

@@

More specifically, the coarseness of a search space partitioning limits the search time within 
a partition, i.e. finely partitioned search spaces require little or no search within a partition 
but offer little placement flexibility. Partitioning can also be fine in one dimension and coarse 
in another to allow flexibility where it is most needed while still ensuring fast finding. For 
example, a hash function can finely partition a low storage tier but each partition can extend 
across multiple tiers so that a search still has to occur in order to find a resource on a particular 
tier.  Specifically, we will address the following research questions:
\begin{tightItemize}
  \item Can we make any guarantees in a scalable decentralized system?; 
 \item  What quality of service metrics can be make guarantees on in a scalable
    way?;
  \item What kind of error rates will we have in our estimation and what error
    rates are acceptable?;
  \item How much will the qos scheduler, admission control, manager cost in
    terms of resources and time?;
  \item  How do we make the scheduler scalable with the size of the system?
\end{tightItemize}

@@

\begin{tightItemize}

@@

\end{tightItemize}
